When are Fuzzy Extractors Possible?

### 2014-09-22 trunk/info-bounds/FuzzyExtPossibility.tex
revisions of distribution aware section

We begin with by showing that fuzzy min-entropy is a sufficient condition in the distribution-aware setting.  We then turn to the standard \emph{distribution oblivious} setting.

@@

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we consider show it is possible to build distribution-aware fuzzy extractors and secure sketches whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

\subsection{Well-Spread Distributions}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
We begin by defining a well-spread distribution.

\begin{definition}
A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
\end{definition}
Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result can be viewed as saying that well-spread distributions are not interesting in the distribution-aware setting.  However, we will show that providing secure sketches for well-spread distributions in the distribution-oblivious setting is impossible.}

\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, m, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, m,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
\end{lemma}  
\begin{proof}
It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
\[
t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
\end{proof}

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}
%We start by considering distributions that have a fixed number of neighbors for each point.
%
%\begin{definition}
%We call a distribution $W$, over metric space $\mathcal{M}$, $(c, t)$-\emph{fixed neighbor} if there exists a constant $c$ such that for all points in $x\in \mathcal{M}$ there are exactly $c$ points $w\in W$ such that $\dis(w, x)\le t$.  We say that $W$ is a $(c, t)$-\emph{bounded neighbor distribution} if for all point $x\in\mathcal{M}$ there are at most $c$ points $w\in W$ such that $\dis(w, x)\le t$.
%\end{definition}
%
%\textbf{Note:} A fixed neighbor distribution is a special case of a bounded-neighbor distribution.
We now present a construction for flat distributions.  We use pairwise-independent hashes:

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
%In other words, $F(K,x_1),F(K,x_2)$ are all uniformly and independently random over $R$. 
\end{definition}

We now show a sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.  The work of Skoric et al.~\cite{skoric2009efficient} use universal hash functions in the setting where there are a polynomial number of possible error patterns.

\begin{construction}
\label{cons:pairwise hash}
Let $W$ be a flat distribution over $\mathcal{M}$.  Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a pairwise independent hash function.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem Sample $K\leftarrow \mathcal{K}$.
\subitem Set $p = F(K, w), K$.
\item $\rec(w', y, K)$:
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}
\begin{lemma}
\consref{cons:pairwise hash} is a $(\mathcal{M}, m, m - \log |R|, t)$-secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:pairwise hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

Note that \consref{cons:pairwise hash} writes down essentially the worst case number of bits in all setting, it knows the maximum number of points in any ball and writes down that number~(with an additional super-logarithmic factor to prevent collisions).  Recall, our hope is to find a sketch that achieves total security equal to the fuzzy min-entropy of the distribution.  Thus, the remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
\]
For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}).  Furthermore, whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ depending on $\Hfuzz(W)$).  That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.  Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.  For a flat distribution, this is also the ball with the largest total weight.  We will see this becomes more difficult as we move to the setting where points have very different probability.  %In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls. We will compensate for this problem by writing down a variable number of bits.
%with a fixed number of neighbors, 
%\begin{align*}
%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
%\end{align*}
%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

\subsection{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:pairwise hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$.  Let $\Hoo(W) \ge m$
Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of pairwise independent hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

>>>>

@@

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors) whenever $\Hfuzz(W)= \omega(\log n)$.
We consider increasingly complex types of distributions and end with an arbitrary distribution over a metric space.  We construct secure sketches but our constructions can be transformed to fuzzy extractors using \lemref{lem:fuzzy ext construction}.  In \secref{sec:dist oblivious} we consider distribution-oblivious algorithms.

\subsection{Well-Spread Distributions}
\bnote{is this section useful?}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
We begin by defining a well-spread distribution.

\begin{definition}
A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
\end{definition}
Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.
\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
\end{lemma}  
\begin{proof}
It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
\[
t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
\end{proof}

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

We now present a construction for flat distributions.  We universal hashes:

\begin{definition}
Let $F : \mathcal{K} \times D \to R$ be a function.  We say that $F$ is \emph{universal} if for all distinct $x_1, x_2 \in D$:
\[
 \Pr_{K \leftarrow \mathcal{K}}[F(K, x_1) = F(K, x_2)] = \frac{1}{|R|} \;.
\]
\end{definition}

A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.  Skoric et al. previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.

\begin{construction}
\label{cons:universal hash}
Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem Sample $K\leftarrow \mathcal{K}$.
\subitem Set $p = F(K, w), K$.
\item $\rec(w', y, K)$:
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}
\begin{lemma}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}
\begin{corollary}
Let $n$ be a security parameter.  
If $|R| \ge |B_{t, max}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log |B_{t, max}| + \omega(\log n)$ suffices.
\end{corollary}

Note that \consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is 
\[
\Hav(W |\sketch(W)) = \Hoo(W) - \log |B_{t, max}| - \omega(\log n)
\]
For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). The achievable security is proportional to the starting entropy minus the largest number of points in any ball.   Whenever $\Hfuzz(W) = \omega(\log n)$, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).  %That is, we can construct a secure sketch whenever there is super-logarithmic starting entropy.  Intuitively, this is because the sketch is deconflicting for the ball with the largest number of points.  For a flat distribution, this is also the ball with the largest total weight.  We will see this becomes more difficult as we move to the setting where points have very different probability.  %In this setting, we may write down a large number of bits to deal with a low weight ball that has a large number of points, but this may completely reveal the high weight balls. We will compensate for this problem by writing down a variable number of bits.
%with a fixed number of neighbors, 
%\begin{align*}
%\Hfuzz(W) &= -\log \max_{x\in \mathcal{M}}, \sum_{w | \dis(w, x)\le t} \Pr[W=w]\\
%&=-\log \max_{x\in \mathcal{M}}, -\log \sum_{w | \dis(w, x)\le t} 2^{-\Hoo(W)}\\
%&= -\log c2^{-\Hoo(W)} = \Hoo(W) - \log c
%\end{align*}
%Thus, the construction is optimal up to a super-logarithmic factor for flat sources with a fixed number of neighbors.  We now attempt to remove both of these restrictions.

\subsection{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:universal hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.  %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.  
An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that layer.  That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$.The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  Note there are $n-m+\ell$ outcomes for $i$ so the overall success of such an adversary is at most $n-m+\ell$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le n+\ell}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+\ell}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
&\le \left(n-m+\ell\right)\left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
&= \left(n-m+\ell\right)\Hfuzz(W)\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+\ell)}$ is at most $2^{-\ell}$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+\ell)}}\Pr[W = w] \le 2^{-\ell}$.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-\ell} + (1-2^{-\ell})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(n+\ell)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le n+\ell} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le n+\ell} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le n+\ell} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{(n-m+\ell) 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(2^{-\ell}+\frac{(1-2^{-\ell})(n-m+\ell)2^{-\Hfuzz(W)}}{2\delta}\right).
\end{align*}
Setting $\ell = m$ yields
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(m+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{m, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

\begin{corollary}
\label{cor:extension to fuzz ext}
Let $n$ be a security parameter and let $\mathcal{M}$ be a metric space such that $\log \log |\mathcal{M}| = O(\log n)$.
For any distribution $W$ over $\mathcal{M}$ with $\Hfuzz(W)=\omega(\log n)$, there exists a $(\mathcal{M}, W, \tilde{m}, t)$-distribution aware secure sketch with $\tilde{m} = \omega(\log n)$ and $\delta = \ngl(n)$.  (Extendible to a fuzzy extractor using~\lemref{lem:fuzzy ext construction}.)
\end{corollary}

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Distribution-Oblivious Sketches}
\label{sec:dist oblivious}
